---
title: "Roman Emperors Statistics"
author: "Monika Piechatzek"
output: html_document
---
```{r}
emperors <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-08-13/emperors.csv")
library(tidyr)
library(ggplot2)
library(tidyverse)
```

# Bar graph showing Birth Province count
Showing the amount of emperors who are born in which province the most
```{r}
ggplot(emperors, aes(birth_prv)) + geom_bar() + xlab("Birth Province") + ylab("Count of Emperors") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

# Bar chart for Rise
Simple bar chart to show what way emperor's rise to power
```{r}
ggplot(emperors, aes(rise)) + geom_bar() + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + xlab("Rise to Power") + ylab("Number of Emperors")
```

# Dot plot for Rise and Birth Province
Simple bar graph that shows an emperor's rise and birth province
```{r}
ggplot(emperors, aes(rise, birth_prv)) + geom_count() + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + xlab("Rise to Power") + ylab("Birth Province")
```

# Color coded Killer labels and Cause and Reign End
Dot plot for cause of death and reign end with color coded killers
```{r}
ggplot(emperors, aes(cause, reign_end, "year", colour = killer)) + geom_point() + theme(legend.position = "bottom") + xlab("Cause of Death") + ylab("Year of End of Reign")
```

#Calculate Age and Cause of Death
Added a column of age of emperor when they passed and reason why they died
```{r}
emperors$birth[is.na(emperors$birth)] <- "0001-01-01" # Remove NA birthdays
emperors$birthage <- format(as.Date(emperors$birth, format="%d/%m/%Y"),"%Y")
emperors$deathage <- format(as.Date(emperors$death, format="%d/%m/%Y"),"%Y")
emperors$birthage <- as.numeric(emperors$birthage)
emperors$deathage <- as.numeric(emperors$deathage)
emperors$age <- ifelse(emperors$birthage > emperors$deathage,  emperors$birthage + emperors$deathage,  emperors$deathage - emperors$birthage)
emperors %>% filter(emperors$age < 99) %>% ggplot(emperors, mapping = aes(y = age, x = reorder(name, age), fill=factor(cause))) + geom_bar(stat = "identity") + coord_flip() + xlab("Emperor") + ylab("Age of Emperor") + guides(fill=guide_legend(title="Cause of Death"))
```
